HerMES: Spatially resolved ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-01-20 LaTeX/ms.tex
Comments from Lingyu Wang
Also added code to compute mass inside einstein radius.

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has identified
    large numbers of dusty star-forming galaxies (DSFGs) over a wide range in
    redshift.  A detailed understanding of these DSFGs is hampered by the poor
    spatial resolution of {\it Herschel}.  We present 870$\,\mu$m 0$\farcs$45
    imaging obtained in Cycle~0 with the Atacama Large Millimeter/submillimeter
    Array (ALMA) of a sample of 29 HerMES DSFGs.  We identify a total of 62
    sources down to the $5\sigma$ limit in our ALMA sample ($\sigma \approx
    0.2\,$mJy).  Optical or near-infrared imaging indicates that 36 of the ALMA
    sources experience a significant flux boost from gravitational lensing ($\mu
    > 1.1$), but only 6 are strongly lensed and show multiple images.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov Chain Monte Carlo visibility plane analysis tool to analyze
    the source properties.  Nearly 70\% of the {\it Herschel} sources break down
    into multiple ALMA counterparts, consistent with previous research
    indicating that the multiplicity rate is high in bright sources discovered
    in sub-mm or FIR surveys with poor spatial resolution.  The ALMA
    counterparts to our {\it Herschel} targets are located much closer to each
    other than ALMA counterparts to sources found in the LABOCA ECDFS
    Submillimeter Survey.  Hydrodynamical numerical simulations and
    semi-analytical models both underpredict the excess in number of sources
    with small separations from each other that is seen in our ALMA sample.
    Combined with our previous work on brighter {\it Herschel} sources, the lens
    models presented here constrain the shape of the intrinsic luminosity
    function for DSFGs to have a break around 8$\,$mJy with a very steep fall
    off at higher flux densities.  The high multiplicity rate and low projected
    separations between sources seen in our sample argue in favor of
    interactions and mergers driving the prodigious emission from the brightest
    DSFGs.

@@

The starting point for the sample selection is source extraction and
photometry.  Sources are detected using the {\sc StarFinder} code
\citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images.
Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},
which allocates flux density based on the 250$\, \mu$m position priors from
{\sc StarFinder}.

>>>>

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  We introduce and make use of {\sc uvmcmcfit}, a
    general purpose and publicly available Markov Chain Monte Carlo visibility
    plane analysis tool to analyze the source properties.  Nearly 70\% of the
    {\it Herschel} sources break down into multiple ALMA counterparts,
    consistent with previous research indicating that the multiplicity rate is
    high in bright sources discovered in sub-mm or FIR surveys with poor
    spatial resolution.  The ALMA counterparts to our {\it Herschel} targets
    are located much closer to each other than ALMA counterparts to sources
    found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
    underpredict the excess in number of sources with small separations from
    each other that is seen in our ALMA sample.  Combined with our previous
    work on brighter {\it Herschel} sources, the lens models presented here
    constrain the shape of the intrinsic luminosity function for DSFGs to have
    a break around 8$\,$mJy with a very steep fall off at higher flux
    densities.  The high multiplicity rate and low projected separations
    between sources seen in our sample argue in favor of interactions and
    mergers driving the prodigious emission from the brightest DSFGs.

@@

The starting point for the sample selection is source extraction and
photometry.  Sources are detected using the {\sc StarFinder} code
\citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images
\citep{Wang:2014lr}.
Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},
which allocates flux density based on the 250$\, \mu$m position priors from
{\sc StarFinder}.
